---
title: "TITLE"
subtitle: "Refugees"
format: 
  revealjs
highlight-style: a11y
execute:
  code-link: true
  echo: true
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
library(dplyr)
library(rvest)
library(httr)
library(readr)
library(readr)
library(RColorBrewer)
library(tidyr)
```


```{r}
#| eval: false
#| echo: false
#| warning: false
#| message: false

## Outline

#* Your presentation should generally follow the same structure as your write-up. 

#* Each team will have 5 minutes for their presentation, and each team member must speak (roughly equally) during this time. 

#* Your presentation will be created using `Quarto`, which allows you to write slides using the same coding structure you’re used to with `Rmarkdown`. 

#* This is a sample Quarto slide template you can edit to your desire to create your presentation. 

## Rubric

#* Roughly I recommend 1 slide for introduction, 2 slides for Question 1, ans 2 slides for Question 2. 
 # + You can imagine spending roughly one minute on each slide.
  #+ You should feel free to have more (or fewer) slides. 
  
#* Your evaluation will be based on your content, professionalism (including sticking to time), and your performance during the Q&A (question and answer). We don’t care how many slides you use to do this.

```

## Introduction {.smaller}

* This data comes from the PopulationStatistics {refugees} R package.

* The package is designed to give people access to the United Nations High Commissioner for Refugees (UNHCR) Refugee Data Finder.

* It provides an easy-to-use interface to the database, which covers forcibly displaced populations.This includes refugees, asylum-seekers, internally displaced people, stateless people, and others over a span of more than 70 years. 
  + The {refugees} package includes eight datasets. 
  + We will specifically be working with population data from 2010 to 2022. 
  + This dataset has 126262 observations and 16 variables. 

## Q1 Graphics
::: panel-tabset

### Q1a
```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.asp: .5

population <- read_csv("data/population.csv")

populations22 <- population %>%
  filter(year == 2022) 

populations22_coo <- populations22 %>%
  group_by(coo_name) %>%
  summarize(total_refugees_and_asylum_seekers = sum(refugees + asylum_seekers))

populations22_coo %>% 
  arrange(-total_refugees_and_asylum_seekers) %>%
  head(n=10) %>%
  ggplot(aes(y=total_refugees_and_asylum_seekers, x = coo_name, fill=coo_name)) +
  geom_col() +
  geom_text(aes(label = total_refugees_and_asylum_seekers), vjust = -0.5, size = 3) + 
  scale_y_continuous(labels = scales::comma_format()) +
  labs(title = "Top 10 Countries of Origin in 2022",
       x = NULL,
       y = "Total Refugees and Asylum Seekers",
       fill = "Country of Origin") +
  scale_fill_brewer( palette = "Spectral")  +
  theme_minimal() +
  theme(axis.text.x = element_blank())

```

### Q1b
```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.asp: .5

populations22_coa <- populations22 %>%
  group_by(coa_name) %>%
  summarize(total_refugees_and_asylum_seekers = sum(refugees + asylum_seekers))

populations22_coa %>% 
  arrange(-total_refugees_and_asylum_seekers) %>%
  head(n=10) %>%
  ggplot(aes(y=total_refugees_and_asylum_seekers, x = coa_name, fill=coa_name)) +
  geom_col() +
  geom_text(aes(label = total_refugees_and_asylum_seekers), vjust = -0.5, size = 3) + 
  scale_y_continuous(labels = scales::comma_format()) +
  labs(title = "Top 10 Countries of Asylum in 2022",
       x = NULL,
       y = "Total Refugees and Asylum Seekers",
       fill = "Country of Asylum") +
  scale_fill_brewer( palette = "Spectral")  +
  theme_minimal() +
  theme(axis.text.x = element_blank())
```

:::



## Q1 Graphics - ALT

```{r, echo=FALSE}
url <- "https://en.wikipedia.org/wiki/List_of_countries_by_population_(United_Nations)"
population <- read_csv("data/population.csv")
#population <- read_csv("project01-team-ashwinmorgenchristopher/data/population.csv")
## Scrape html and store table

#Grab all the tables and then navigate to the one you wanted.
tables <- url %>%
  read_html() %>%
  html_nodes(css = "table")

#Grab the specific table
wiki_country_pop_tbl <- html_table(tables[[1]], fill = TRUE) %>%
  filter(row_number() > 1)
colnames(wiki_country_pop_tbl)[4] <- "Population"
wiki_country_pop_tbl <- select(wiki_country_pop_tbl, 'Location', 'Population')
wiki_country_pop_tbl[wiki_country_pop_tbl == 'China[a]'] <- 'China'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Tanzania[b]'] <- 'Tanzania'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'France[c]'] <- 'France'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Spain[d]'] <- 'Spain'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Ukraine[e]'] <- 'Ukraine'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Australia[f]'] <- 'Australia'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Ukraine[e]'] <- 'Ukraine'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Somalia[h]'] <- 'Somalia'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Taiwan[g]'] <- 'Taiwan'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Netherlands[i]'] <- 'Netherlands'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Portugal[j]'] <- 'Portugal'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Hong Kong (China)[k]'] <- 'Hong Kong'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Serbia[l]'] <- 'Serbia'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Finland[m]'] <- 'Finland'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Norway[n]'] <- 'Norway'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Palestine[o]'] <- 'Palestine'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Georgia[p]'] <- 'Georgia'
wiki_country_pop_tbl[wiki_country_pop_tbl == 'Moldova[q]'] <- 'Moldova'
wiki_country_pop_tbl$Population = parse_number(wiki_country_pop_tbl$Population, )



colnames(population)[colnames(population) == 'coo_name'] <- "Location"
populations_wiki_coo <- merge(population, wiki_country_pop_tbl, by = "Location")

colnames(population)[colnames(population) == 'Location'] <- 'coo_name'
colnames(population)[colnames(population) == 'coa_name'] <- 'Location'
populations_wiki_coa <- merge(population, wiki_country_pop_tbl, by = "Location")
```

::: panel-tabset

### Q1a
```{r, eval=F}
#| echo: false
#| warning: false
#| message: false
#| fig.asp: .5

populations22 <- population %>%
  filter(year == 2022) 

populations22_coo <- populations22 %>%
  group_by(coo) %>%
  summarize(total_refugees_and_asylum_seekers = sum(refugees + asylum_seekers))

populations22_coa <- populations22 %>%
  group_by(coa) %>%
  summarize(total_refugees_and_asylum_seekers = sum(refugees + asylum_seekers))



populations22_wiki_o <- populations_wiki_coa %>%  #The population with respect to the origin
  filter(year == "2022") %>%
  group_by(Location) %>%
  summarize(total__refugees_leaving_origin = sum(refugees + asylum_seekers))

populations22_wiki_a <- populations_wiki_coo %>%  #The population with respect to the asylum
  filter(year == "2022") %>%
  group_by(Location) %>%
  summarize(total__refugees_arriving_asylum = sum(refugees + asylum_seekers))

populations22_wiki_coo <- populations22_wiki_o %>%
  group_by(coo) %>%
  summarize(pop_div_refugee = Population / total__refugees_leaving_origin)

populations22_wiki_coa <- populations22_wiki_a %>%
  group_by(coa) %>%
  summarize(pop_div_refugee = Population / total__refugees_arriving_asylum)



populations22_coo %>% 
  arrange(-total_refugees_and_asylum_seekers) %>%
  head(n=10) %>%
  ggplot(aes(y=total_refugees_and_asylum_seekers, x = coo, fill=coo)) +
  geom_col()

```

### Q1b
```{r, eval=F}
#| echo: false
#| warning: false
#| message: false
#| fig.asp: .5

test <- populations_wiki_coo %>%
  group_by(Population) %>%
  summarize(total_refugees_and_asylum_seekers = sum(refugees + asylum_seekers))%>%
  filter(row_number() < 167) %>%  #removing India and China
  filter(row_number() != 142) #removing Afghanistan

#Ethiopia is still sort of an outlier

ggplot(test, aes(y=total_refugees_and_asylum_seekers, x = Population)) + geom_point()
```

populations22_coa %>% 
  arrange(-total_refugees_and_asylum_seekers) %>%
  head(n=10) %>%
  ggplot(aes(y=total_refugees_and_asylum_seekers, x = coa, fill=coa)) +
  geom_col()

### Q1c
```{r, eval=F}
#| echo: false
#| warning: false
#| message: false
#| fig.asp: .5

populations22_wiki_coo %>% 
  arrange(pop_div_refugee) %>%
  head(n=20) %>%
  ggplot(aes(y=pop_div_refugee, x = reorder(coo, pop_div_refugee)), layer(size = 2)) +  geom_point() + labs(x="Countries", y = "")
```

### Q1d
```{r, eval=F}
#| echo: false
#| warning: false
#| message: false
#| fig.asp: .5

tibble()

populations22_wiki_coa %>% 
  arrange(-pop_div_refugee) %>%
  head(n=10) %>%
  ggplot(aes(y=pop_div_refugee, x = coa, fill=coa)) + geom_col()
```

:::




## Question 2
How have refugee populations changed in Turkey over time?

## Question 2

::: panel-tabset

### Graph 1
```{r}
#| echo: false
#| warning: false
#| message: false

tur_all <- population %>% 
  filter(coa == "TUR") %>%
  group_by(year) %>%
  summarise(ref_count = sum(refugees + asylum_seekers + returned_refugees + idps + returned_idps + stateless + ooc))

tur_all %>%
  group_by(year) %>%
  ggplot(aes(x = year, y = ref_count)) +
  geom_point(size = 5, alpha = .5) +
  geom_smooth() +
  scale_y_continuous(trans = 'log10', labels = scales::trans_format("log10", format = scales::math_format(10^.x))) +
  labs(title = "All Refugees in Turkey Over Time",
       x = "Year",
       y = "Number of Total Refugees") +
    theme_minimal()
```


### Graph 2
```{r}
#| echo: false
#| warning: false
#| message: false

custom_blue_palette <- brewer.pal(n = 8, name = "Blues")[3:8]

tur_decade <- population %>% 
  filter(coa == "TUR") %>%
  mutate(decades = case_when(
    between(year, 1950, 1959) ~ "1950s",
    between(year, 1960, 1969) ~ "1960s",
    between(year, 1970, 1979) ~ "1970s",
    between(year, 1980, 1989) ~ "1980s",
    between(year, 1990, 1999) ~ "1990s",
    between(year, 2000, 2009) ~ "2000s",
    between(year, 2010, 2019) ~ "2010s",
    between(year, 2020, 2029) ~ "2020s"))

tur_decade_sum <- tur_decade%>%
  group_by(decades) %>%
  summarise(refugees = sum(refugees),
            asylum_seekers = sum(asylum_seekers),
            returned_refugees = sum(returned_refugees),
            stateless = sum(stateless),
            ooc = sum(ooc)) %>%
  pivot_longer(!decades, names_to = "condition", values_to = "count")



tur_decade_sum %>%
  ggplot(aes(x = decades, y = count, fill = condition)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_y_continuous(trans = 'log10', labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  labs(title = "Refugee Demographics in Turkey Over Time",
       x = "Decade",
       y = "Count",
       fill = "Refugee Categories") +
  scale_fill_brewer(palette = "Set2", labels = c(
    "refugees" = "Refugees",
    "asylum_seekers" = "Asylum Seekers",
    "returned_refugees" = "Returned Refugees",
    "stateless" = "Stateless Persons",
    "ooc" = "Others of Concern to UNHCR"
  ))  +
    theme_minimal()
```

:::