---
title: "TITLE"
subtitle: "Refugees"
format: 
  revealjs
highlight-style: a11y
execute:
  code-link: true
  echo: true
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
library(dplyr)
library(rvest)
library(httr)
library(readr)
library(readr)
library(RColorBrewer)
library(tidyr)
```


```{r}
#| eval: false
#| echo: false
#| warning: false
#| message: false

## Outline

#* Your presentation should generally follow the same structure as your write-up. 

#* Each team will have 5 minutes for their presentation, and each team member must speak (roughly equally) during this time. 

#* Your presentation will be created using `Quarto`, which allows you to write slides using the same coding structure you’re used to with `Rmarkdown`. 

#* This is a sample Quarto slide template you can edit to your desire to create your presentation. 

## Rubric

#* Roughly I recommend 1 slide for introduction, 2 slides for Question 1, ans 2 slides for Question 2. 
 # + You can imagine spending roughly one minute on each slide.
  #+ You should feel free to have more (or fewer) slides. 
  
#* Your evaluation will be based on your content, professionalism (including sticking to time), and your performance during the Q&A (question and answer). We don’t care how many slides you use to do this.

```

## Introduction {.smaller}

* This data comes from the PopulationStatistics {refugees} R package.

* The package is designed to give people access to the United Nations High Commissioner for Refugees (UNHCR) Refugee Data Finder.

* It provides an easy-to-use interface to the database, which covers forcibly displaced populations.This includes refugees, asylum-seekers, internally displaced people, stateless people, and others over a span of more than 70 years. 
  + The {refugees} package includes eight datasets. 
  + We will specifically be working with population data from 2010 to 2022. 
  + This dataset has 126262 observations and 16 variables. 

## Question 1

In the year 2022, how did geography affect refugee populations? Where are refugees coming from and where are they going to?



## Question 1 Graphics
::: panel-tabset

### Graph 1
```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.asp: .5

population <- read_csv("data/population.csv")

populations22 <- population %>%
  filter(year == 2022) 

populations22_coo <- populations22 %>%
  group_by(coo_name) %>%
  summarize(total_refugees = sum(refugees + asylum_seekers + returned_refugees + stateless + ooc))

populations22_coo %>% 
  arrange(-total_refugees) %>%
  head(n=10) %>%
  ggplot(aes(y=total_refugees, x = coo_name, fill=coo_name)) +
  geom_col() +
  geom_text(aes(label = total_refugees), vjust = -0.5, size = 3) + 
  scale_y_continuous(labels = scales::comma_format()) +
  labs(title = "Top 10 Countries of Origin in 2022",
       x = NULL,
       y = "Total Refugees and Asylum Seekers",
       fill = "Country of Origin") +
  scale_fill_brewer( palette = "Spectral")  +
  theme_minimal() +
  theme(axis.text.x = element_blank())

```

### Graph 1

Top 3 countries of origin 
  + Afghanistan
  + Syria 
  + Ukraine 
  
4th country almost thrice as small

Correlates with the events:

- Taliban control Afghanistan

- Syrian conflict

- Russo-Ukranian war

### Graph 2
```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.asp: .5

populations22_coa <- populations22 %>%
  group_by(coa_name) %>%
   summarize(total_refugees = sum(refugees + asylum_seekers + returned_refugees + stateless + ooc))

populations22_coa %>% 
  arrange(-total_refugees) %>%
  head(n=10) %>%
  ggplot(aes(y=total_refugees, x = coa_name, fill=coa_name)) +
  geom_col() +
  geom_text(aes(label = total_refugees), vjust = -0.5, size = 3) + 
  scale_y_continuous(labels = scales::comma_format()) +
  labs(title = "Top 10 Countries of Asylum in 2022",
       x = NULL,
       y = "Total Refugees and Asylum Seekers",
       fill = "Country of Asylum") +
  scale_fill_brewer( palette = "Spectral")  +
  theme_minimal() +
  theme(axis.text.x = element_blank())
```

### Graph 2 

Top 3 countries of Asylum are Turkey, Iran, and Venezuela 
  
The data have a more even spread.

Three main types of countries of asylum:

1. Near a country with some hardship (Turkey, Bangladesh, Poland)

2. Near many countries with some hardship (Uganda)

3. A good place to seek refuge (Germany, U.S.A.)


:::


## Question 2
How have refugee populations changed in Turkey over time?



## Question 2 Graphics

::: panel-tabset

### Graph 1
```{r}
#| echo: false
#| warning: false
#| message: false

tur_all <- population %>% 
  filter(coa == "TUR") %>%
  group_by(year) %>%
  summarise(ref_count = sum(refugees + asylum_seekers + returned_refugees + stateless + ooc))

tur_all %>%
  group_by(year) %>%
  ggplot(aes(x = year, y = ref_count)) +
  geom_point(size = 3, alpha = .8) +
  geom_smooth() +
  scale_y_continuous(trans = 'log10', labels = scales::trans_format("log10", format = scales::math_format(10^.x))) +
  labs(title = "All Refugees in Turkey Over Time",
       x = "Year",
       y = "Number of Total Refugees") +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12)) 
```

### Graph 1
The general trend of refugees in Turkey is one of growth. 

The rate of growth is faster than exponential. 

Most of the growth occurs right after 2010.

The rate of natural population growth should be a straight line on a log graph. This represents significant outside factors on the influx of Turkish refugees.

Influx after 2010 is likely due to Syrian refugees. This is reflected in current data which shows over 3.3 million syrian refugees in Turkey as of 2023.


### Graph 2
```{r}
#| echo: false
#| warning: false
#| message: false

custom_blue_palette <- brewer.pal(n = 8, name = "Blues")[3:8]

tur_decade <- population %>% 
  filter(coa == "TUR") %>%
  mutate(decades = case_when(
    between(year, 1950, 1959) ~ "1950s",
    between(year, 1960, 1969) ~ "1960s",
    between(year, 1970, 1979) ~ "1970s",
    between(year, 1980, 1989) ~ "1980s",
    between(year, 1990, 1999) ~ "1990s",
    between(year, 2000, 2009) ~ "2000s",
    between(year, 2010, 2019) ~ "2010s",
    between(year, 2020, 2029) ~ "2020s"))

tur_decade_sum <- tur_decade%>%
  group_by(decades) %>%
  summarise(refugees = sum(refugees),
            asylum_seekers = sum(asylum_seekers),
            returned_refugees = sum(returned_refugees),
            stateless = sum(stateless),
            ooc = sum(ooc)) %>%
  pivot_longer(!decades, names_to = "condition", values_to = "count")



tur_decade_sum %>%
  filter(count > 0) %>%
  ggplot(aes(x = decades, y = count, fill = condition)) +
  geom_bar(stat = "identity", position = "stack") +
   scale_y_continuous(trans = 'log10') +
  geom_text(aes(label = count), position = position_stack(vjust = 0.5), size = 3) +
  labs(title = "Refugee Demographics in Turkey Over Time",
       x = "Decade",
       y = "Count",
       fill = "Refugee Categories") +
  scale_fill_brewer(palette = "Set2", labels = c(
    "refugees" = "Refugees",
    "asylum_seekers" = "Asylum Seekers",
    "returned_refugees" = "Returned Refugees",
    "stateless" = "Stateless Persons",
    "ooc" = "Others of Concern to UNHCR"
  ))  +
    theme_minimal() +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_blank()) 
```

### Graph 2
Refugees makes up the bulk of refugee demographics throughout time.

Big jump in Asylum Seekers and Returned Refugees during and after 2010.

The majority of rufugees in Turkey have historically been Refugees with Asylum Seekers also making up a large portion of the total starting in the 2000s. 

Others of Concern to the UNHCR see a brief spike in the 2000s and 2010s. 

:::