---
title: "Refugee Project Proposal"
format: html
editor: visual
---

# Proposal

Your proposal should include:

-   A brief description of your dataset including its provenance, dimensions, etc. (Make sure to load the data and use inline code for some of this information.)
-   The reason why you chose this dataset.
-   The two questions you want to answer.
    -   A plan for answering each of the questions including the variables involved, variables to be created (if any), external data to be merged in (if any).

------------------------------------------------------------------------

```{r}
library(tidyverse)
library(refugees)

populations <- refugees::population

write_csv(populations, "data/population.csv")
```

```{r}
dim(populations)

populations
```

| variable          | class     | description                                                     |
|--------------|--------------|--------------------------------------------|
| year              | double    | The year.                                                       |
| coo_name          | character | Country of origin name.                                         |
| coo               | character | Country of origin UNHCR code.                                   |
| coo_iso           | character | Country of origin ISO code.                                     |
| coa_name          | character | Country of asylum name.                                         |
| coa               | character | Country of asylum UNHCR code.                                   |
| coa_iso           | character | Country of asylum ISO code.                                     |
| refugees          | double    | The number of refugees.                                         |
| asylum_seekers    | double    | The number of asylum-seekers.                                   |
| returned_refugees | double    | The number of returned refugees.                                |
| idps              | double    | The number of internally displaced persons.                     |
| returned_idps     | double    | The number of returned internally displaced persons.            |
| stateless         | double    | The number of stateless persons.                                |
| ooc               | double    | The number of others of concern to UNHCR.                       |
| oip               | double    | The number of other people in need of international protection. |
| hst               | double    | The number of host community members.                           |

Dataset summary:

There are 126,262 observations in the dataset, and there are 16 variables. 10 of the variables are numerical and 6 are categorical.

Why we chose this dataset:

We chose this set because we are interested in the consequences of real world policy. The dataset also is quite clean and has a good distribution of numeric and categorical variables making it ideal for analysis.

Research Questions:

1.  *How does geography affect refugee populations in 2022? Where are refugees coming from and where are they going to?*
    -   Variables involved: coo_name (Country of Origin Name), coa_name (Country of Asylum Name), refugees, asylum_seekers, idps, stateless (numeric variables indicating the number of people in each category)

    -   Variables to be created: a combined variable, total_refugees_and_asylum_seekers, to represent the total number of refugees and asylum seekers from each country of origin to each country of asylum.
2.  *How have refugee populations changed in North America over time?*
    -   Variables involved: year, coa_name (focusing on countries in North America), refugees, asylum_seekers, returned_refuges, idps, stateless

    -   Variables to be created: total_population_affected, combining refugees, asylum seekers, returned refugees, IDPs, and stateless persons for a comprehensive view over time.

------------------------------------------------------------------------
