---
title: "Refugee Project Proposal"
format: html
editor: visual
---

# Proposal

Your proposal should include:

-   A brief description of your dataset including its provenance, dimensions, etc. (Make sure to load the data and use inline code for some of this information.)
-   The reason why you chose this dataset.
-   The two questions you want to answer.
    -   A plan for answering each of the questions including the variables involved, variables to be created (if any), external data to be merged in (if any).

```{r}
library(tidyverse)
library(refugees)

populations <- refugees::population

write_csv(populations, "data/population.csv")
```

```{r}
dim(populations)

populations
```

| variable          | class     | description                                                     |
|-------------------|-----------|-----------------------------------------------------------------|
| year              | double    | The year.                                                       |
| coo_name          | character | Country of origin name.                                         |
| coo               | character | Country of origin UNHCR code.                                   |
| coo_iso           | character | Country of origin ISO code.                                     |
| coa_name          | character | Country of asylum name.                                         |
| coa               | character | Country of asylum UNHCR code.                                   |
| coa_iso           | character | Country of asylum ISO code.                                     |
| refugees          | double    | The number of refugees.                                         |
| asylum_seekers    | double    | The number of asylum-seekers.                                   |
| returned_refugees | double    | The number of returned refugees.                                |
| idps              | double    | The number of internally displaced persons.                     |
| returned_idps     | double    | The number of returned internally displaced persons.            |
| stateless         | double    | The number of stateless persons.                                |
| ooc               | double    | The number of others of concern to UNHCR.                       |
| oip               | double    | The number of other people in need of international protection. |
| hst               | double    | The number of host community members.                           |

Why we chose this dataset:

We chose this dataset because we are interested in the consequences of real world policy. The dataset is also quite clean, and has a good distribution of numeric and categorical variables making it ideal for analysis.
We wanted to best connect what we learn in this class with real world applications, and this dataset seemed like the best fit.

Research Questions:

1.  How does geography affect refugee populations in 2022? Where are refugees coming from and where are they going to?
2.  How have refugee populations changed in North America over time?
